Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2017-12-01 paper-ieee-trans.tex

Software developers involved in these projects have learnt over time how to make their product more reliable in order to satisfy requirements of different communities, such as physics and bio-informatics.

>>>>

Software developers involved in these projects over time have learned  how to make their final products more reliable in order to satisfy requirements of different communities, such as physics.
